APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-28 paper.tex
Finish writing appendix.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{appendix}
\usepackage{geometry}

\usepackage{bera}
\usepackage{listings}
\usepackage{xcolor}
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}
\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}
\usepackage[framed, numbered]{matlab-prettifier}

@@

\begin{document}

@@

\section{Code}

@@

\section{Input Files}

\section{Output Files}

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{appendix}
\usepackage{geometry}
\usepackage{csvsimple}
\usepackage[table]{xcolor}
\usepackage{fancyhdr}

\usepackage{bera}
\usepackage{listings}
\colorlet{punct}{red!60!black}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{delim}{RGB}{20,105,176}
\colorlet{numb}{magenta!60!black}
\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{background},
    literate=
     *{0}{{{\color{numb}0}}}{1}
      {1}{{{\color{numb}1}}}{1}
      {2}{{{\color{numb}2}}}{1}
      {3}{{{\color{numb}3}}}{1}
      {4}{{{\color{numb}4}}}{1}
      {5}{{{\color{numb}5}}}{1}
      {6}{{{\color{numb}6}}}{1}
      {7}{{{\color{numb}7}}}{1}
      {8}{{{\color{numb}8}}}{1}
      {9}{{{\color{numb}9}}}{1}
      {:}{{{\color{punct}{:}}}}{1}
      {,}{{{\color{punct}{,}}}}{1}
      {\{}{{{\color{delim}{\{}}}}{1}
      {\}}{{{\color{delim}{\}}}}}{1}
      {[}{{{\color{delim}{[}}}}{1}
      {]}{{{\color{delim}{]}}}}{1},
}
\usepackage[framed, numbered]{matlab-prettifier}

@@

\begin{document}
\pagestyle{fancy}

@@

\newpage
\section{Input Files}\label{app:input_files}

\newpage
\section{Output Files}\label{app:output_files}

Output tables of solved truss models in Appendix \ref{app:input_files}.

\csvstyle{nodeTableStyle}{tabular=| r r r r r r r |,
    table head=\hline \rowcolor{brown!50} \bfseries Node \# &
        \bfseries x & \bfseries y & \bfseries z &
        \bfseries dx & \bfseries dy & \bfseries dz,
    late after head=\\\hline\hline,
    head to column names,
    before table=\rowcolors{2}{white!25}{gray!50},
    late after last line={\\\hline}}

\csvstyle{elementTableStyle}{tabular=| r r r r r r |,
    table head=\hline \rowcolor{brown!50} \bfseries Element \# &
        \bfseries Material & \bfseries Node 1 & \bfseries Node 2 &
        \bfseries Stress & \bfseries Force,
    late after head=\\\hline\hline,
    head to column names,
    before table=\rowcolors{2}{white!25}{gray!50},
    late after last line={\\\hline}}

\subsection{sample\_001}\label{app:tables/sample_001}

\noindent
\csvreader[nodeTableStyle]{tables/sample_001_nodes.csv}{}
    {\node & \x & \y & \z & \dx & \dy & \dz}%
\vspace{1em}

\noindent
\csvreader[elementTableStyle]{tables/sample_001_elements.csv}{}
    {\element & \material & \firstnode & \secondnode & \stress & \force}%
\vspace{1em}

\subsection{sample\_002}\label{app:tables/sample_002}

\noindent
\csvreader[nodeTableStyle]{tables/sample_002_nodes.csv}{}
    {\node & \x & \y & \z & \dx & \dy & \dz}%
\vspace{1em}

\noindent
\csvreader[elementTableStyle]{tables/sample_002_elements.csv}{}
    {\element & \material & \firstnode & \secondnode & \stress & \force}%
\vspace{1em}

\subsection{sample\_003}\label{app:tables/sample_003}

\noindent
\csvreader[nodeTableStyle]{tables/sample_003_nodes.csv}{}
    {\node & \x & \y & \z & \dx & \dy & \dz}%
\vspace{1em}

\noindent
\csvreader[elementTableStyle]{tables/sample_003_elements.csv}{}
    {\element & \material & \firstnode & \secondnode & \stress & \force}%
\vspace{1em}

\subsection{sample\_004}\label{app:tables/sample_004}

\noindent
\csvreader[nodeTableStyle]{tables/sample_004_nodes.csv}{}
    {\node & \x & \y & \z & \dx & \dy & \dz}%
\vspace{1em}

\noindent
\csvreader[elementTableStyle]{tables/sample_004_elements.csv}{}
    {\element & \material & \firstnode & \secondnode & \stress & \force}%
\vspace{1em}

\subsection{baltimore\_truss}\label{app:tables/baltimore_truss}

\noindent
\csvreader[nodeTableStyle]{tables/baltimore_truss_nodes.csv}{}
    {\node & \x & \y & \z & \dx & \dy & \dz}%
\vspace{1em}

\noindent
\csvreader[elementTableStyle]{tables/baltimore_truss_elements.csv}{}
    {\element & \material & \firstnode & \secondnode & \stress & \force}%
\vspace{1em}

\newpage
\section{Code}\label{app:code}

@@
